Bitmap Indexing for Fast Analysis of Large Datasets

### 2016-03-29 ms/ms.tex
Abstract first pass

%---------------------------------------------------------------------------------
% ABSTRACT
\begin{abstract}
Current scientific datasets can reach unwieldy sizes that impede analysis and scientific discovery. We present a method for using bitmap indexes to map files within a dataset to take advantage of domain partitioning across multiple files and limit the volume of data that must be loaded into memory. 
\todo{more...}
\end{abstract}

@@

%There is a slight increase in the time required to identify files when ghost zones are included, even though no files are selected by ghost zones along except for an index order of 6.

@@

%---------------------------------------------------------------------------------
% COMMENTS
\newpage
\todo{To do:
\begin{itemize}
\item Improve introduction \& conclusion
\item Find \& add tagged references.
\item Acknowledgements
\item Write abstract
\item Switch times for tests to be averages over 10 runs (with std. dev. error bars?)
\item Make diagram showing buffer added to test datasets?
\item Plot \% files identified vs. \% domain selected?
\end{itemize}
}

>>>>

%---------------------------------------------------------------------------------
% ABSTRACT
\begin{abstract}
Current scientific datasets can reach unwieldy sizes that impede analysis and scientific discovery. We present a method for using Morton order bitmap indexes to map the parts of the full domain touched by files within a dataset. This takes advantage of domain partitioning across multiple files and limits the volume of data that must be loaded into memory. This method is tested on mock datasets containing $1024^3$ three-dimensional points split across 512 files according to different partitioning schemes. Using Morton order bitmap indexes for localized partitioning schemes like the Hilbert space-filling curve, the number of files that must be loaded to access data for a sub-section of the domain will scale with the size of the sub-section. This will dramatically decrease the time and memory required for loading data during analysis.
\end{abstract}

@@

@@

%---------------------------------------------------------------------------------
% COMMENTS
\newpage
\todo{To do:
\begin{itemize}
\item Improve introduction \& conclusion
\item Find \& add tagged references.
\item Acknowledgements
\item Write abstract
\item Switch times for tests to be averages over 10 runs (with std. dev. error bars?)
\item Make diagram showing buffer added to test datasets?
\item Plot \% files identified vs. \% domain selected?
\item Ensure plot labels are all the same size when in document (set widths to colsize)
\end{itemize}
}
